### 2015-10-26 docs/prelim_analysis.Rmd
updates rec fxn in IBM with sqrt(cover); appears to be working now

Figures
-------
```{r read_data, echo=FALSE, eval=F}
output_list <- readRDS("../results/ipm_comp_nocomp_sims.RDS")
mlist <- melt(output_list)
```

>>>>

Figures
-------
```{r concept_fig, echo=FALSE, eval=T}
library(png)
library(grid)
img <- readPNG("./prelim_analysis_files/synchrony_conceptual_fig.png")
grid.raster(img)
```

```{r read_data, echo=FALSE, eval=F}
output_list <- readRDS("../results/ipm_comp_nocomp_sims.RDS")
mlist <- melt(output_list)
```
